
\begin{itemize}

\item[] 	% ictm2022
\emph{46th World Conference of the International Council for Traditional Music -- ICTM2022},
Lisboa, Portugal, 21 al 27 de julio, 2022.
Luis Jure y Martín Rocamora: presentación oral del artículo
``Micro-timing in Uruguayan Candombe Drumming''.

\item[] 	% SoMoS2022
\emph{Second Symposium of the ICTM Study Group on Sound, Movement, and the Sciences, SoMoS 2022},
Barcelona, España, 26 al 28 de octubre, 2022.
Luis Jure: presentación oral del artículo
``Documentation and analysis of Uruguayan candombe drumming''.

\item[] 	% aawm2022
\emph{Seventh International Conference on Analytical Approaches to World Music, 2022},
Sheffield, Reino Unido, 14 al 17 de junio, 2022.
Luis Jure: presentación oral (a distancia) del artículo
``The piano drum style of Gustavo Oviedo, candombe master drummer''.

\item[] 	% aawm2021
\emph{Sixth International Conference on Analytical Approaches to World Music (AAWM 6)},
París, Francia, 9 al 12 de junio, 2021.
Luis Jure: presentación oral (a distancia) del póster
``Tempo, Micro-tempo and Dynamics in Uruguayan Candombe Drumming''.

\item[]	% aawm2019
\emph{First Analytical Approaches to World Music Special Topics Symposium},
Birmingham, Reino Unido, 2 al 4 de julio, 2019.
Luis Jure: presentación oral del artículo
``\texttt{carat}: A toolbox for computer--aided rhythm analysis''.

\item[]	% fma2018
\emph{8\textsuperscript{th} International Workshop on
Folk Music Analysis -- FMA 2018},
Thessaloniki, Grecia, 26 al 29 de junio, 2018.
Luis Jure: presentación oral del artículo ``\emph{Subir la llamada}:
Negotiating tempo and dynamics in Uruguayan Candombe drumming''.

\item[]	% aawm2018
\emph{Fifth International Conference on Analytical Approaches
to World Music -- AAWM 2018},
Thessaloniki, Grecia, 26 al 29 de junio, 2018.
Luis Jure: presentación oral del artículo ``Improvisation techniques of the
\emph{repique} drum in Uruguayan Candombe drumming''.

\item[] 	% RRPW 2017
\emph{16\textsuperscript{th} Rhythm Production and Perception Workshop -- RPPW 2017},
Birmingham, Inglaterra, 3 al 5 de julio, 2017.
Luis Jure: presentación por póster del artículo ``Clave patterns in Uruguayan Candombe drumming''.

\item[]	% ICTM 2017
\emph{44\textsuperscript{th} International Council for Traditional Music World Conference -- ICTM 2017},
Limerick, Irlanda, 13 al 19 de julio, 2017.
Luis Jure: presentación oral del artículo ``Timeline patterns in Uruguayan Candombe drumming''.

\item[] 	% aawm2016
\emph{Fourth International Conference on Analytical Approaches
to World Music -- AAWM 2016},
Nueva York, Estados Unidos, 8 al 11 de junio, 2016.
Luis Jure: presentación oral del artículo ``Microtiming in the Rhythmic
Structure of Candombe Drumming Patterns''.

\item[] 	% ismir2015
\emph{16\textsuperscript{th} International Society for Music Information Retrieval
Conference -- ISMIR 2015}, Málaga, España, 26 al 30 de octubre, 2015.
Luis Jure y Martín Rocamora: presentación oral del artículo
``Beat and Downbeat Tracking Based on Rhythmic Patterns
Applied to the Uruguayan Candombe Drumming''.

\item[]	% cictem2015
\emph{Congreso Internacional de Ciencia y Tecnología Musical -- CICTeM 2015},
Buenos Aires, Argentina, 17 al 19 de septiembre, 2015.
Luis Jure y Martín Rocamora: presentación oral del artículo
``An audio--visual database of Candombe performances for computational
musicological studies''.

\item[]	% cim2014
\emph{9\textsuperscript{th} Conference on Interdisciplinary Musicology -- CIM14}.
Berlín, Alemania, 4 al 6 de diciembre, 2014.
Luis Jure y Martín Rocamora: presentación oral del artículo
``Tools for detection and classification of piano drum
patterns from candombe recordings''.

\end{itemize}

