\documentclass[a4paper]{article}
\usepackage{url} 
\usepackage{natbib}

\begin{document}

\title{Eventos Proyecto Cando} 
\author{}
\date{}
\maketitle

\subsection*{Conference/Congreso}
\input{congresos}

\subsection*{Keynote}

\begin{itemize}

\item[]	% XXXX
``Some Title"
Presentación en ``Interpersonal Entrainment in Music Performance Workshop''.
Some place, some date.\\
Martín Rocamora.

\end{itemize}

\subsection*{Colloquium/Coloquio}

\begin{itemize}

\item[]	% coloquio 2021
``Proyecto \emph{`Documentación y Análisis del Candombe Uruguayo'}:
un enfoque desde la musicología computacional''.
Presentación en el ``Encuentro de Investigación en Música y Sonido''.
Escuela Universitara de Música, Universidad de la República.
Montevideo, Uruguay, 15 de octubre, 2021.\\
Luis Jure.

\item[ ]	% coloquio2011
``Principios generativos del toque del repique del Candombe''.
Presentación en el coloquio \emph{La música entre África y América}, Centro Nacional de Documentación
Musical Lauro Ayestarán del Ministerio de Educación y Cultura.
Montevideo, Uruguay, 3 de octubre, 2011.\\
Luis Jure.

\item[ ]	% columbia2010
``Drums and the City. Musical traits and performance
practices of Candombe in Montevideo''.
Presentación en el coloquio \emph{Sounding the Space}.
Columbia University. 
Nueva York, Estados Unidos, 8 de octubre, 2010.\\
Luis Jure.

\end{itemize}

\subsection*{Workshop}

\begin{itemize}

\item[]	% IEMP2018
``Some insights/perspectives on interpersonal
entraniment in candombe drumming''.
Presentación en el ``Interpersonal Entrainment in Music Performance Workshop''.
Génova, Italia, 8 de marzo, 2018.\\
Luis Jure, Martín Rocamora.

\item[]	% IEMP2016
``An audio--visual database of Candombe performances
for computational musicological studies''.
Presentación en el ``Interpersonal Entrainment in Music Performance Workshop''.
Durham, Reino Unido, 15 de mayo, 2016.\\
Luis Jure, Martín Rocamora.

\end{itemize}

\subsection*{Talk/Conferencia}

\begin{itemize}

\item[ ]	% MDW2022
Institut für Volksmusikforschung und Ethnomusikologie, Universität für Musik und darstellende Kunst Wien.
``Musical Traits and Performance Practice of Uruguayan Candombe Drumming:
A Computational Musicological Approach''.
Viena, Austria, 19 de octubre, 2022.\\
Luis Jure.

\item[ ]	% MaxPlanck2022
Max Planck Institute for Empirical Aesthetics.
``A computational approach to Uruguayan Candombe drumming''.
Fránfort del Meno, Alemania, 10 de agosto, 2022.\\
Luis Jure, Martín Rocamora.

\item[ ]	% stanford2018
Stanford University, Center for Computer Research in Music and Acoustics -- CCRMA.
``Musical Traits and Performance Practice of Uruguayan Candombe Drumming:
A Computational Musicological Approach''.
Palo Alto, California, Estados Unidos, 14 de noviembre, 2018.\\
Luis Jure.

\item[ ]	% ucdavis2018
University of California, Davis, Department of Music.
``Musical Traits and Performance Practice of Uruguayan Candombe Drumming:
A Computational Musicological Approach''.
Davis, California, Estados Unidos, 8 de noviembre, 2018.\\
Luis Jure.

\item[ ]	% columbia2017
Columbia University, Computer Music Center.
``Uruguayan Candombe drumming -- Musical traits and performance practice:
A case study for computational musicology''.
Nueva York, Estados Unidos, 13 de diciembre, 2017.\\
Luis Jure.

\item[ ]	% tu2017
Technische Universität Berlin, Fachgebiet Audiokommunikation.
``Uruguayan Candombe drumming -- Musical traits and performance practice:
A case study for computational musicology''.
Berlín, Alemania, 11 de abril, 2017.\\
Luis Jure.

\item[ ]	% ofai2014
Österreichisches Forschungsinstitut für Artificial Intelligence -- OFAI.
``Tools for detection and classification of piano drum patterns from Candombe recordings''.
Viena, Austria, 12 de diciembre, 2014.\\
Luis Jure.

\item[ ]	% ofai2013
Österreichisches Forschungsinstitut für Artificial Intelligence -- OFAI.
``Rhythmic pattern analysis: the Uruguayan Candombe drumming as a case study''
Viena, Austria, 19 de noviembre, 2013.\\
Luis Jure.

\item[ ]	% cictem2013
\emph{Congreso Internacional de Ciencia y Tecnología Musical -- CICTeM 2013}.
``Detección automática de patrones rítmicos: el Candombe uruguayo como caso de estudio''.
Buenos Aires, Argentina, 26 al 28 de septiembre, 2013.\\
Luis Jure, Martín Rocamora.

\end{itemize}

\subsection*{Outreach/Extensión}

\begin{itemize}

\item[]	% IEMP2018
``Registros de Ansina''.
Presentación en el taller ``Ansina Tradición -- Transmisión, no imposición''.
Casa de la Cultura Afrouruguaya 
Montevideo, Uruguay 4 de mayo, 2019.\\
Luis Jure.

\end{itemize}

\end{document}

